\documentclass[11pt,margin,line]{res}
\usepackage{palatino}
\usepackage[pdftex]{graphicx}
\usepackage[usenames,dvipsnames]{color}
%% \input{colordefs}
\usepackage[pdftitle={Venkatesh Choppella's CV},%
pdfauthor={Venkatesh Choppella},%
linkcolor=black,%
colorlinks=true,% true
citecolor=black,%blue,%
urlcolor=Brown,%navy%
]{hyperref}


%\pagecolor{lightgoldenrodyellow}
%% \color{Gray}
% see http://www.sci.usq.edu.au/staff/robertsa/LaTeX/usecolour.html
% on how to use the following predefined colors

%% GreenYellow, Yellow, Goldenrod, Dandelion, Apricot, Peach,
%% Melon, YellowOrange, Orange, BurntOrange, Bittersweet,
%% RedOrange, Mahogany, Maroon, BrickRed, Red, OrangeRed,
%% RubineRed, WildStrawberry, Salmon, CarnationPink, Magenta,
%% VioletRed, Rhodamine, Mulberry, RedViolet, Fuchsia, Lavender,
%% Thistle, Orchid, DarkOrchid, Purple, Plum, Violet, RoyalPurple,
%% BlueViolet, Periwinkle, CadetBlue, CornflowerBlue, MidnightBlue,
%% NavyBlue, RoyalBlue, Blue, Cerulean, Cyan, ProcessBlue, SkyBlue,
%% Turquoise, TealBlue, Aquamarine, BlueGreen, Emerald,
%% JungleGreen, SeaGreen, Green, ForestGreen, PineGreen, LimeGreen,
%% YellowGreen, SpringGreen, OliveGreen, RawSienna, Sepia, Brown,
%% Tan, Gray


%% \color{MidnightBlue}

%\pagecolor{snow}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}



% From
% http://notfaq.wordpress.com/2006/10/04/latex-customize-page-numbering/

% Requires total page count to be known in advance.

%% \usepackage{fancyhdr}
%% \pagestyle{fancy}
%% \fancyhf{} % clear all header and footer fields
%% \fancyfoot[R]{\footnotesize Page \thepage\ of 8}
%% \renewcommand{\headrulewidth}{0pt}
%% \renewcommand{\footrulewidth}{0pt}


% page n of m works with the res class only if you make the
% following fix in res.cls:

% comment the \nofiles line.  By commenting it, you ensure
% that the .aux file is generated.

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\fancyhf{} % clear all header and footer fields
%\fancyhead[RO,LE]{\footnotesize Venkatesh Choppella}
%% \fancyfoot[R]{\footnotesize Venkatesh Choppella}
%% \fancyfoot[R]{\footnotesize Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[RO,LE]{\footnotesize  \href{http://www.iiitmk.ac.in/\~choppell}{Venkatesh Choppella}\\ Page \thepage\ of \pageref{LastPage}}
\fancyfoot[LO,RE]{\footnotesize \today}


\begin{document}

\name{Venkatesh Choppella \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{3in}}
International Institute of Information  Technology  & {\it Voice:}+91 965-274-0281\\
Hyderabad                     &{\it Fax:}    +91-40-6653 1413\\
GachiBowli, Hyderabad        & {\it E-mail:}  venkatesh.choppella@iiit.ac.in\\ 
Andhra Pradesh 500 032, INDIA            & %\hspace{-4em}\url{http://www.iiitmk.ac.in/~choppell}%
\\     
%  {www.iiitmk.ac.in/{\textasciitilde}choppell}
\end{tabular}

%% \begin{tabular}{@{}p{3.5in}p{3in}}
%% Computer Science and Engineering & 
%% {\it Voice:}  +1-614-915-4090 (m) \\
%% Ohio State University                         & {\it Fax:}    +1-614-292-2911 \\
%% 395 Dreese Labs                               & {\it E-mail:}  choppell@gmail.com\\ 
%% Columbus, OH 43210 USA
%%            & {\it WWW:}
%% \href{http://www.iiitmk.ac.in/~choppell}{www.iiitmk.ac.in/{\textasciitilde}choppell}\\
%% \end{tabular}

%% \section{\sc Objective}
%% Teaching, Research and Development in Software Engineering,
%% Information Technology and Computer Science.

\section{\sc Areas of Interest and research}
Software Architectures, Web technologies, Programming
Languages, Formal specification and verification of systems,
Computer Science Education

\section{\sc Education}
{\bf Indiana University}, Bloomington, Indiana, USA\\
%{\em Department of Computer Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. in Computer Science, Aug 2002
\end{list1}

{\bf Indian Institute of Technology, Madras}, Chennai, India\\
%{\em Department of Computer Science and Engineering} 
\vspace*{-.1in}
\begin{list1}
\item[] M.Tech., Computer Science and Engineering,  May, 1987
\end{list1}

{\bf Indian Institute of Technology, Kanpur}, Kanpur, India\\
%{\em Department of Computer Science and Engineering} 
\vspace*{-.1in}
\begin{list1}
\item[] B.Tech., Computer Science and Engineering,  May, 1985. %CPI 7.8/10.0
\end{list1}

\section{\sc Employment}

% To add extra space between roww
% http://www.cs.toronto.edu/~scalosub/latextips.html

%% % Adds a space between the text and the [T]op \hline
\newcommand\T{\rule{0pt}{2.8ex}}

%% % Adds a space between the text and the [B]ottom \hline
%% \newcommand\B{\rule[-1.7ex]{0pt}{0pt}}

\begin{tabular}{lllcrr}
{\em Associate Professor}, IIIT Hyderabad & {\bf
  Jan} & {\bf 2010\/} & {\bf -} &  & \T\\
{\em Associate Professor,} Indian Inst. of Info. Tech.\&
  Mgmt Kerala  & {\bf Oct\/} & {\bf 2003\/} & {\bf -} &\T\\
{\em Post-Doctoral Researcher}, Oak Ridge National
  Laboratory & {\bf Dec\/} & {\bf 2002\/} & {\bf -\/}  & {\bf Sep\/} &
  {\bf 2003\/}\T\\ %10mo
{\em  Senior Software Engineer}, Hewlett-Packard Company & 
{\bf Jan\/} &  {\bf 2001\/} & {\bf -\/}  & {\bf Aug\/} & {\bf
  2001\/}\T\\ %8mo
 {\em Research Staff}, Indiana University &
{\bf Mar\/} & {\bf 2000\/} & {\bf -}  & {\bf Dec\/} & {\bf
  2000\/}\T\\%9mo
{\em Senior S/W Engineer}, Xerox Corporation & {\bf
  Sep} & {\bf 1999\/} &  {\bf -}  & {\bf Feb\/} & {\bf 2000\/}\T\\%4mo
\end{tabular}

\section{\sc Employment Contd.}
\begin{tabular}{lllcrr}
{\em Research Staff}, Derivation Systems & {\bf
  Jun\/} & {\bf 1995\/} &  {\bf -\/}  & {\bf May\/} & {\bf
  1997\/}\T\\ %24mo
{\em Research/Teaching Associate} Indiana University & {\bf Aug}
  & {\bf 1988\/} &  {\bf -\/}  & {\bf Jan\/} & {\bf 1995\/}\T\\ %36mo
{\em S/W Engineer} CMC Ltd & {\bf Mar} & {\bf 1987\/} &  {\bf
  -\/}  & {\bf Aug\/} & {\bf 1988\/}\T%17mo
\end{tabular}

\vspace{3em}

\section{\sc Visiting Appointments}
\begin{tabular}{lllcrr}
{\em Visiting Associate Professor}, IIIT Hyderabad & {\bf
  Jul} & {\bf 2009\/} & {\bf -} & {\bf Dec } & {\bf 2009}\T\\
{\em Visiting Associate Professor}, IIIT Bangalore & {\bf
  Jul} & {\bf 2009\/} & {\bf -} & {\bf Apr } & {\bf 2010}\T\\
{\em Visiting Research Associate}, Ohio State University & {\bf
  May} & {\bf 2005\/} & {\bf -} & {\bf May } & {\bf 2006}\T\\
\end{tabular}

\section{\sc Recent/Selected Publications}

Krishna Chaitanya Telikicherla and Venkatesh Choppella.
{\bf Enabling the Development of Safer Mashups for Open
  Data}.  Proceedings of the 1st International Workshop on
Inclusive Web Programming - Programming on the Web with Open
Data for Societal Applications.  (IWP 2014).  Jun 2014.
ACM.

Gollapudi VRJ Sai Prasad, T. B. Dinesh, Venkatesh Choppella.
{\bf Overcoming the new accessibility challenges using the
  sweet framework} Proceedings of the 11th Web for All
Conference.  (W4A '14).  ACM

Himanshu Zade, Santosh Adimoolam, Sai Gollapudi, Anind Dey
and Venkatesh Choppella.  {\bf Edit Distance modulo
  Bisimulation: A Quantitative Measure to Study Evolution of
  User Models}.  Proceedings of the ACM Conference on
Computer Human Interaction (CHI) 2014.

Krishna Chaitanya Telikicherla and Venkatesh Choppella.
{\bf Alloy model for {C}ross {O}rigin {R}equest {P}olicy
  (CORP)}.  IIIT Hyderabad Tech Report IIIT/TR/2013/31.  2013



Ankur Goel, Venkatesh Choppella.  {\bf State based access
  control for open e-governance}.  Proceedings of the 7th
International Conference on Theory and Practice of
Electronic Governance.  (ICEGOV '13).  2013.  ACM

T B Dinesh and Venkatesh Choppella.  {\bf A case for
  process-driven models for e-governance architectures}.
7th International Conference on E-Governance.  22 - 24
Apr 2010.  Bangalore, India.  

V.~Choppella, A.~Sengupta, E.~L. Robertson and
S.~D.~Johnson.  {\bf Preliminary Explorations in Specifying
  and Validating Entity-Relationship Models in PVS.}
Proceedings of AFM~07, ACM Workshop on Applied Formal
Methods, Nov.~6th,~2007, Atlanta, USA.  Preprint available
at \url{http://fm.csl.sri.com/AFM07/afm07-preprint.pdf}.

V. Choppella.  {\bf Polymorphic Type Reconstruction Using
Type Equations.}  In {\em {Implementation of Functional
Languages 15th International Workshop, IFL 2003, Edinburgh,
UK, Sep~2003 Revised Papers}}.  Springer Lecture Notes in
Computer Science, Vol. 3145, pp.~53--68, 2004.

V.~Choppella and C.~T. Haynes. {\bf Source-tracking
  Unification}.  In {\em {Proceedings of 19th International
    Conference on Automated Deduction, (CADE-19), Miami
    Beach, USA, Aug~2003}} Springer Lecture Notes in
Artificial Intelligence, Vol. 2741, pp.~458--472, 2003.


% \section{\sc Journal and Conference Submissions}

% Philip Bradford and Venkatesh Choppella.  Fast Semi-Dyck
% Constrained Shortest Paths.  Submitted for review. 

\vspace{2em}

%% \section{\sc Papers in preparation}
%% % J. B. White, V. Choppella, D. E. Bernholdt.  Monadic synthesis
%% % of the NAS Multi-grid Benchmark.

%% Venkatesh Choppella.  {\bf Variable-free canonical forms for
%% Tensor Expressions}.

%% Venkatesh Choppella and Guillaume Marceau.  {\bf Graph Embeddings
%% for diagnosing Hindley-Milner type reconstruction}.

%% \section{\sc Papers under review}

%% Venkatesh Choppella and T B Dinesh.  {\bf FOSS, Web 2.0 and
%%   Mashups as a Natural Learning Management Infrastructure}.
%% Tutorial proposal submitted to the 2nd IEEE Conference on
%% Technology for Education, Mumbai, Jul 2010.


%% Venkatesh Choppella {\bf A case for Subversion in Academia}.
%% Submitted to the 2nd IEEE Conference on Technology for
%% Education, Mumbai, Jul 2010.

\vspace{2em}


\vspace{2em}

\newpage


% \section{\sc Thesis Supervision}

% {\em Automatic generation and deployment of Network
%   Configuration scripts}.
% Gangadhar~Chalapaka. Post-Graduate Diploma in Information
% Technology (PGDIT), IIITM-K 2009 (Expected).

% {\em Rebuilding the Institute Network}.  V.~Asha~ Rose,
% Girish~N~Gopal, Mithu~Mary~Kuruvilla.  MSIT, IIITM-K 2008.

% {\em Building Instructional Technologies and Content for the
%   Course Principles of Programming Course}.  Girish~N~Gopal,
% Mithu~Mary~Kuruvilla.  MSIT, IIITM-K 2008. 

% {\em Automatic Generation of Formal Specification of
%   Entity-Relationship Diagrams}.  Alice~Joseph.  M.Tech
% Vellore Institute of Technology 2008.  External Supervisor.

% {\em Modeling Point Mutations in E-Coli Gene and their
%   effect on fitness over successive generations}.
% Nithya~Sam and Vimi~Soman.  Masters in Information
% Technology (MSIT), IIITM-K 2007.  

% {\em IT support for Palliative Care services with an
%   e-learning platform and an electronic health record.}
% Cibi Chacko, K.~Rejoy Bhaskar, V.~R.~Lekshmi and I.~Subha.
% MSIT, IIITM-K 2007.

% {\em Detecting system-breakins by comparing correlated
%   frequency matrices}.  Anju~Pratap.  M.Tech. Computer
% Science, Alagappa University 2007.  External Supervisor.

% \section{\sc Thesis Supervision Contd.}


% {\em Police Portal for Community Interaction: General
%   Category Manipulation and Alert System}.  Jeena Premkumar.
% Post Graduate Diploma in Information Technology (PGDIT),
% IIITM-K 2005.

% {\em Formal Specification of Police Portal's Complaint
%   Module using Z and OCL}.  Sangram~Jena and Manish~Garg.
% PGDIT, IIITM-K 2005. 

% {\emph{Web Services for Agricultural Marketing System}}.
% K.~M.~Manu~Prathab and P.~Roopiga.  MSc Computer Science,
% Kerala University 2004.

% {\em Implementation of Efficient Algorithms for Unification
%   Debugging}.  M.~T.~Chitra and V.~G.~Suman.  MSc. Computer
% Science, Kerala University 2004.


\section{Workshops and Tutorials conducted}

Introduction to Aspect-Oriented Design and Programming.
{\bf Invited Tutorial}.  {\em Thirteenth International
  Conference on Advanced Computing and Communications,
  Coimbatore, India, Dec~14th,~2005}.  With Anurag
Mendhekar.

Principles of Programming for Web 2.0.  2 week Summer School
at IIIT Hyderabad for college teachers.  May 3rd--14th.
IIIT Hyderabad.  With T B Dinesh.


\vspace{2em}

\section{\sc Patents}

Cristina Lopes, Gregor Kiczales, John Lamping, Erik Hilsdale,
Venkatesh Choppella, and Taher Haveliwala.
\href{http://www.patentstorm.us/patents/6473895.html}
{Aspect-Oriented System Monitoring and Tracing}.  {\em {U.S.
    Patent No. 09/357,508.}} Filed 1999. Awarded April 2002.

% \newpage
\section{\sc Awards}

\href{http://www.manthanaward.com/winner2005.asp}{All India
Manthan Awards} Second Prize in the E-Governance category
for coordinating the Trivandrum City Police Portal for
Community Interaction \url{www.tvmcitypolice.org}, New
Delhi, India,~2005.

Best Paper Award. International Parallel and Distributed
Processing Symposium (IPDPS), Albuquerque, New Mexico,
USA,~2004.

% \newpage

Best Paper Award  (Systems). Internationl Conference on High
Performance Computing (HiPC), Hyderabad, India,~2003.

DuPont Fellowship, Computer Science Dept., Indiana
University,~1988.

Merit Certificate for performance in the Joint Entrance
Examination, IIT Kanpur,~1981.

%\newpage

\section{\sc Grants}

Virtual Labs Phase 2, MHRD, Govt of India.  Approx. 70
Crores over three years (Expected July 2014).  National
Integration Coordinator and responsible for deliverery of
Engineering backend (Approx. 15 Crores over three years).

Linneaus Palme Award for faculty exchange between
Malardaalen University Sweden and IIIT Hyderabad.  2014.
(80,000 SEK, approx.  8 Lakh INR).

Research Grant from Siemens India Ltd.  2012-2013.
Approx. 16 Lakhs.  Pincipal Invesigator.

European Commission.  Erasmus Mundus External Cooperation
Window. European Research and Educational Collaboration with
Asia Project for Academic Mobility 2008-2009.
\url{http://www.mrtc.mdh.se/eureca/}.  Institute
Coordinator.  10,000 Euro.

\newpage

\section{\sc Grants Contd.}
Ministry of Information Technology, Government of India.
Information Security Education and Awareness (ISEA)
2006-2011.  Principal Investigator at Participating
Institution IIITM-K.  Rs. 300,000 per annum. 

Government of Kerala.  Police Portal for Community
Interaction 2004-2005.  Rs. 2,900,000.  Co-investigator.

\section{\sc Consulting}

Cognizant Technologies.  Chennai, India.  December
2007-January 2008.

Satyam Computers.  Hyderabad, India.  April 2008.

Servelots Infotech.  Bangalore, India.  Since December 2007

Indian Postal Service.   New Delhi, India.  May 2009

Terumo Penpol Ltd.  Trivandrum, India.  December 2008

\vspace{2em}

\section{\sc Professional Service}

Programme committee member, 1st International workshop on
Web-supported concurrent collaborative work.  (WSCCW 2010),
Hong Kong.  December 2010.

Programme committee member, 4th ACM International Conference
on theory and practice of e-governance (ICEGOV 2010),
Beijing, China.  November 2010.

Reviewer and Examiner, Design and Development of Robot
Design Platform and Database Research Platform and Database
based Robot Software Development Framework.  MS Thesis by
Subhash S. IIIT Hyderbad.  May 2010

Programme committee member, 11th International Conference on
Distributed Computing and Internet Technologies (ICDCIT)
February, 2011, Bhubaneswar, India.

Reviewer,  Formal Methods in System Design.  Springer, 2010.

Programme committee member, 4th India Software Engineering
Conference (ISEC) February, 2011, Thiruvananthapuram, India.

Programme committee member, 10th International Conference on
Distributed Computing and Internet Technologies (ICDCIT)
February, 2010, Bhubaneswar, India.

Programme committee member and reviewer, International
Conference on Software Engineering Education and Training
(CSEET) Feb 17-19, 2009, Hyderabad, India.

% Heap Reference Analysis by Amay Karkare

External reviewer for PhD Thesis, Computer Science, Indian
Institute of Technology, Bombay, Jan 2009.

Convener, Institute Information Technology and Services
Committee, IIITM-K.  Mar 2008 - Jan 2009.

Member, committee appointed by Kerala State IT Mission,
Govt.~of Kerala, to implement Public Key Infrastructure in
state government offices, 2008.


Reviewer, Journal of Parallel and Distributed Computing.
Elsevier. Aug 2008.

\newpage

\section{\sc Professional Service Contd.}

Reviewer, International Journal of Formal Computing.
Springer. Aug 2008.

Organizer, Free Map Workshop, IIITM-K, Feb 2008. 

Organizer, One day workshop on Pantoto: Building Information
Management Systems for Small and Medium Enterprises. 
IIITM-K, Feb 2008.


Programme and Organizing Committee member, IEEE workshop on
Connecting Computer Science to Domains, IIITM-K.  Dec~2007.

Convener, Institute Academic Affairs Committee, IIITM-K.
Aug 2006 - July 2007.


Moderator, Panel on Computer Science Teaching, National
workshop on Technology Enhanced Learning, Trivandrum,
Kerala, India.  Jan 5th-6th, 2007.

Panelist, Scilab in Science and Engineering Education.
Indo-French Workshop on Scilab, IIT Bombay.  Mar~8th,~2007.

Organizer, IEEE/CSI Workshop on Community Wireless
Networking, Trivandrum, Kerala, India, Dec 1st-2nd, 2006.

Programme Committee member, International Conference on
Advanced Computing and Communications (ADCOMM~05),
Coimbatore, India, Dec 14-17, 2005.

Programme Committee member, Free Software, Free Society: Three
nation conference on Free, Libre and Open Source Software,
Trivandrum India, May 2005.

Board Member, SPACE (Society for Promotion of Alternative
Computing and Employment), NGO for promoting Free and Open
Source Software in Kerala. Since 2004.

Anonymous referee for The Fifth International Conference on
Parallel and Distributed Computing, Applications and
Technologies (PDCAT~04), 2004.  

Acknowledged by the authors of the following books for
proof reading, comments  and technical assistance:\\
\begin{list2}
 \item G. Springer and D. P. Friedman.  {Scheme and the Art of
 Programming}.  {\em {MIT Press,~1989}}.
%%  \vspace{0.5em}
 \item D.P. Friedman, M. Wand and C.T. Haynes.  Essentials of
 Programming Languages, 1st Edition  {\em {MIT Press,~1991}}.
%%  \vspace{0.5em}
 \item Raymond Smullyan. G\"{o}del's Incompleteness Theorems.
 {\em {Oxford University Press,~1992}}.
%%  \vspace{0.5em}
 \item Jon Barwise and Lawrence S. Moss. Vicious Circles
 {\em {CSLI Stanford,~1997}}.
\end{list2}

% \section{\sc Programming Experience} 
% \begin{list2}

% \item Languages: Fortran, Lisp, C, Scheme, ML, Haskell,
%   Prolog, Java, Python, Javascript

% \item Internet Technologies:  J2EE, Spring, Ruby on Rails, Web 2.0

% \item Theorem Provers:  PVS

% \item Operating Systems:  Unix/Linux, Windows
% \end{list2}

\vspace{2em}

\section{\sc Professional Membership}

Computer Society of India

Indian Association for Research in Computer Science

\section{\sc Citizenship}
Citizen of India

\section{\sc Date of Birth}
Available upon request.

\section{\sc Languages}
English, Hindi, Telugu

\section{\sc References}
Available upon request.



\end{resume}
\end{document}




