\documentclass[11pt,margin,line]{res}
\usepackage{palatino}
\usepackage[pdftex]{graphicx}
\usepackage[usenames,dvipsnames]{color}
%% \input{colordefs}
\usepackage[pdftitle={Venkatesh Choppella's CV},%
pdfauthor={Venkatesh Choppella},%
linkcolor=black,%
colorlinks=true,% true
citecolor=black,%blue,%
urlcolor=Brown,%navy%
]{hyperref}


%\pagecolor{lightgoldenrodyellow}
%% \color{Gray}
% see http://www.sci.usq.edu.au/staff/robertsa/LaTeX/usecolour.html
% on how to use the following predefined colors

%% GreenYellow, Yellow, Goldenrod, Dandelion, Apricot, Peach,
%% Melon, YellowOrange, Orange, BurntOrange, Bittersweet,
%% RedOrange, Mahogany, Maroon, BrickRed, Red, OrangeRed,
%% RubineRed, WildStrawberry, Salmon, CarnationPink, Magenta,
%% VioletRed, Rhodamine, Mulberry, RedViolet, Fuchsia, Lavender,
%% Thistle, Orchid, DarkOrchid, Purple, Plum, Violet, RoyalPurple,
%% BlueViolet, Periwinkle, CadetBlue, CornflowerBlue, MidnightBlue,
%% NavyBlue, RoyalBlue, Blue, Cerulean, Cyan, ProcessBlue, SkyBlue,
%% Turquoise, TealBlue, Aquamarine, BlueGreen, Emerald,
%% JungleGreen, SeaGreen, Green, ForestGreen, PineGreen, LimeGreen,
%% YellowGreen, SpringGreen, OliveGreen, RawSienna, Sepia, Brown,
%% Tan, Gray


%% \color{MidnightBlue}

%\pagecolor{snow}
\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in
\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}



% From
% http://notfaq.wordpress.com/2006/10/04/latex-customize-page-numbering/

% Requires total page count to be known in advance.

%% \usepackage{fancyhdr}
%% \pagestyle{fancy}
%% \fancyhf{} % clear all header and footer fields
%% \fancyfoot[R]{\footnotesize Page \thepage\ of 8}
%% \renewcommand{\headrulewidth}{0pt}
%% \renewcommand{\footrulewidth}{0pt}


% page n of m works with the res class only if you make the
% following fix in res.cls:

% comment the \nofiles line.  By commenting it, you ensure
% that the .aux file is generated.

\usepackage{fancyhdr}
\pagestyle{fancy}
\usepackage{lastpage}
\fancyhf{} % clear all header and footer fields
%\fancyhead[RO,LE]{\footnotesize Venkatesh Choppella}
%% \fancyfoot[R]{\footnotesize Venkatesh Choppella}
%% \fancyfoot[R]{\footnotesize Page \thepage\ of \pageref{LastPage}}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
\fancyfoot[RO,LE]{\footnotesize  \href{http://www.iiitmk.ac.in/\~choppell}{Venkatesh Choppella}\\ Page \thepage\ of \pageref{LastPage}}
\fancyfoot[LO,RE]{\footnotesize \today}


\begin{document}

\name{Venkatesh Choppella \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{3.5in}p{3in}}
International Institute of Information  Technology  & {\it Voice:}+91 939-699-4506\\
Hyderabad                     &{\it Fax:}    +91-40-6653 1413\\
GachiBowli, Hyderabad        & {\it E-mail:}  choppell@gmail.com\\ 
Andhra Pradesh 500 032, INDIA            & %\hspace{-4em}\url{http://www.iiitmk.ac.in/~choppell}%
\\     
%  {www.iiitmk.ac.in/{\textasciitilde}choppell}
\end{tabular}

%% \begin{tabular}{@{}p{3.5in}p{3in}}
%% Computer Science and Engineering & 
%% {\it Voice:}  +1-614-915-4090 (m) \\
%% Ohio State University                         & {\it Fax:}    +1-614-292-2911 \\
%% 395 Dreese Labs                               & {\it E-mail:}  choppell@gmail.com\\ 
%% Columbus, OH 43210 USA
%%            & {\it WWW:}
%% \href{http://www.iiitmk.ac.in/~choppell}{www.iiitmk.ac.in/{\textasciitilde}choppell}\\
%% \end{tabular}

%% \section{\sc Objective}
%% Teaching, Research and Development in Software Engineering,
%% Information Technology and Computer Science.

\section{\sc Interests}
Software Architectures, Web technologies, Programming
Languages, Formal specification and verification of systems,
Computer Science Education

\section{\sc Education}
{\bf Indiana University}, Bloomington, Indiana, USA\\
%{\em Department of Computer Science} 
\vspace*{-.1in}
\begin{list1}
\item[] Ph.D. in Computer Science, Aug 2002
\begin{list2}
\vspace*{.05in}
\item Dissertation:  ``Unification Source-tracking with
  Application to Diagnosis of Type Inference'' 
\item Advisor:  Christopher T. Haynes
\end{list2}
\vspace*{.05in}
\item[] M.S., Computer Science,  May 1995,
\end{list1}

{\bf Indian Institute of Technology, Madras}, Chennai, India\\
%{\em Department of Computer Science and Engineering} 
\vspace*{-.1in}
\begin{list1}
\item[] M.Tech., Computer Science and Engineering,  May, 1987
\begin{list2}
\vspace*{.05in}
\item Dissertation:  ``Implementation of ML using the SECD
  machine'' 
\item Advisor: C.~R.~Muthukrishnan
\end{list2}
\end{list1}

{\bf Indian Institute of Technology, Kanpur}, Kanpur, India\\
%{\em Department of Computer Science and Engineering} 
\vspace*{-.1in}
\begin{list1}
\item[] B.Tech., Computer Science and Engineering,  May, 1985. %CPI 7.8/10.0
\end{list1}

\section{\sc Employment}

% To add extra space between roww
% http://www.cs.toronto.edu/~scalosub/latextips.html

%% % Adds a space between the text and the [T]op \hline
\newcommand\T{\rule{0pt}{2.8ex}}

%% % Adds a space between the text and the [B]ottom \hline
%% \newcommand\B{\rule[-1.7ex]{0pt}{0pt}}

\begin{tabular}{lllcrr}
{\em Associate Professor}, IIIT Hyderabad & {\bf
  Jan} & {\bf 2010\/} & {\bf -} &  & \T\\
{\em Visiting Associate Professor}, IIIT Hyderabad & {\bf
  Jul} & {\bf 2009\/} & {\bf -} & {\bf Dec } & {\bf 2009}\T\\
{\em Visiting Associate Professor}, IIIT Bangalore & {\bf
  Jul} & {\bf 2009\/} & {\bf -} & {\bf Apr } & {\bf 2010}\T\\
{\em Visiting Research Associate}, Ohio State University & {\bf
  May} & {\bf 2005\/} & {\bf -} & {\bf May } & {\bf 2006}\T\\
{\em Associate Professor,} Indian Inst. of Info. Tech.\&
  Mgmt Kerala  & {\bf Oct\/} & {\bf 2003\/} & {\bf -} &\T\\
{\em Adjunct Faculty,} Tata
  Consultancy Services  & {\bf Nov\/} &  {\bf 2003\/} & {\bf
  -\/}  & {\bf Nov\/} &   {\bf 2005\/}\T\\ %6mo
{\em Post-Doctoral Researcher}, Oak Ridge National
  Laboratory & {\bf Dec\/} & {\bf 2002\/} & {\bf -\/}  & {\bf Sep\/} &
  {\bf 2003\/}\T\\ %10mo
{\em PhD. Candidate}, Indiana University & {\bf
  Sep\/} & {\bf 2001\/} & {\bf -\/}  & {\bf Jul\/} & {\bf 2002\/}\T\\
{\em  Senior Software Engineer}, Hewlett-Packard Company & 
{\bf Jan\/} &  {\bf 2001\/} & {\bf -\/}  & {\bf Aug\/} & {\bf
  2001\/}\T\\ %8mo
 {\em Research Staff}, Indiana University &
{\bf Mar\/} & {\bf 2000\/} & {\bf -}  & {\bf Dec\/} & {\bf
  2000\/}\T\\%9mo
{\em Senior S/W Engineer}, Xerox Corporation & {\bf
  Sep} & {\bf 1999\/} &  {\bf -}  & {\bf Feb\/} & {\bf 2000\/}\T\\%4mo
{\em PhD. Candidate}, Indiana University & {\bf
  Jan\/} & {\bf 1999\/} &  {\bf -\/}  & {\bf Sep\/} & {\bf 1999\/}\T\\
\end{tabular}
\newpage

\section{\sc Employment Contd.}
\begin{tabular}{lllcrr}
{\em Research Staff}, Derivation Systems & {\bf
  Jun\/} & {\bf 1995\/} &  {\bf -\/}  & {\bf May\/} & {\bf
  1997\/}\T\\ %24mo
{\em Research/Teaching Associate} Indiana University & {\bf Aug}
  & {\bf 1988\/} &  {\bf -\/}  & {\bf Jan\/} & {\bf 1995\/}\T\\ %36mo
{\em S/W Engineer} CMC Ltd & {\bf Mar} & {\bf 1987\/} &  {\bf
  -\/}  & {\bf Aug\/} & {\bf 1988\/}\T%17mo
\end{tabular}


\vspace{3em}

\section{\sc Teaching Experience}

{\bf Institutes of Information Technology, Trivandrum, Bangalore and Hyderabad}
\vspace{-.5cm}

{\em Associate Professor} \hfill {\bf Oct 2003 - present}\\
Designing and teaching the following courses in computer
science and information technology.

\vspace*{1em}

\begin{list2}
\item Principles of Programming Languages, 2009, 2010
\item Principles of Programming  2007, 2008, 2009
\item Web Technologies  2003, 2004, 2006, 2007, 2008
\item Interpreters and Compilers 2004.
\item Mathematical Foundations of Information Technology 2004.
\item Introduction to Databases 2005, 2006
\item Data Structures 2009
\item Computer Networks  2008 (Associate Instructor)
\item Scientific Computing 2006 (Associate Instructor)
\item Computational Biology 2007 (Co-Instructor)
\end{list2}

%\vspace{-.1cm}
%\section{\sc Teaching Experience Contd.}

{\bf Indiana University Computer Science},
Bloomington, Indiana, USA

\vspace{-.5cm}

{\em Associate Instructor} \hfill {\bf Jan 1990 - Jan 1995}\\
Graded assignments, conducted discussions, and
shared lecturing responsibilities for the following courses:

%% undergraduate courses in
%% programming languages, data structures, and algorithms, and
%% graduate courses in programming language semantics.  Courses
%% assisted. 

\vspace*{.05in}  
\begin{list2}
\item Introduction to Programming with C and Scheme
\item Introduction to Data Structures
\item Introduction to Algorithms
\item Introduction to Programming Languages 
\item Semantics of Programming Languages
\end{list2}

%\vspace{-.1cm}

%\vspace{-.1cm}

\section{\sc Refereed Workshop and Conference Publications}

T B Dinesh and Venkatesh Choppella.  {\bf A case for
  process-driven models for e-governance architectures}.
7th International Conference on E-Governance.  22 - 24
April, 2010, Bangalore, India.  Accepted for publication.

Venkatesh Choppella and K~R~Srivathsan.  {\bf Fostering
  Community Interaction with the Trivandrum City Police
  Portal.}  3rd ACM International Conference on the Theory
and Practice of E-Governance, Bogota, Colombia, pp 365--368,
Nov 2009.

V.~Choppella, A.~Sengupta, E.~L. Robertson and
S.~D.~Johnson.  {\bf Preliminary Explorations in Specifying
  and Validating Entity-Relationship Models in PVS.}
Proceedings of AFM~07, ACM Workshop on Applied Formal
Methods, Nov.~6th,~2007, Atlanta, USA.  Preprint available
at \url{http://fm.csl.sri.com/AFM07/afm07-preprint.pdf}.

Albert Hartono, Qingda Lu, Xiaoyang Gao, Sriram
Krishnamoorthy, Marcel Nooijen, Gerald Baumgartner,
Venkatesh Choppella, David Bernholdt, Russell Pitzer,
J. Ramanujam, Atanas Rountev, and P. Sadayappan.  {\bf
Identifying Cost-Effective Common Subexpressions to Reduce
Operation Count in Tensor Contraction Evaluations.}
International Conference on Computational Science (ICCS'06),
LNCS 3991, pages 267-275, May 2006.  Copyright 2006
Springer-Verlag.

S.~Krishnan, S.~Krishnamoorthy, G.~Baumgartner, C-C.~Lam,
J.~Ramanujam, P.~Sadayappan and V.~Choppella.  {\bf
Efficient Synthesis of Out-of-core Algorithms Using a
Nonlinear Optimization Solver.}  In {\em
{Proc. International Parallel and Distributed Processing
Symposium, Albuquerque, New Mexico, USA, Apr~2004}}.
(Proceedings available on CD-ROM).  IEEE Computer Society.

A.~Bibireata, S.~Krishnan, G.~Baumgartner, D.~Cociorva,
C-C.~Lam, P.~Sadayappan, J.~Ramanujam, D.~E.~Bernholdt and
V.~Choppella.  {\bf Memory-constrained Data Locality
Optimizations for Tensor Contractions.}  In {\em {Proc. 16th
International Workshop on Languages and Compilers for
Parallel Computing (LCPC '03), College Station, Texas, Oct
2003}}.  Springer Lecture Notes in Computer Science
Vol. 2958, pp.~93--108, 2004.

V. Choppella.  {\bf Polymorphic Type Reconstruction Using
Type Equations.}  In {\em {Implementation of Functional
Languages 15th International Workshop, IFL 2003, Edinburgh,
UK, Sep~2003 Revised Papers}}.  Springer Lecture Notes in
Computer Science, Vol. 3145, pp.~53--68, 2004.

S. Krishnan, S. Krishnamoorthy, G. Baumgartner, D. Cociorva,
C. Lam, P.  Sadayappan, J. Ramanujam, D. E. Bernholdt, and
V. Choppella.  {\bf Data Locality Optimization for Synthesis
of Efficient Out-of-Core Algorithms}. In {\em {Proc. of the
Intl. Conf. on High Performance Computing, Hyderabad, India,
Dec~2003}}.  Springer Lecture Notes in Computer Science,
Vol.~2913 pp.~406--417, 2003.

V.~Choppella and C.~T. Haynes. {\bf Source-tracking
  Unification}.  In {\em {Proceedings of 19th International
    Conference on Automated Deduction, (CADE-19), Miami
    Beach, USA, Aug~2003}} Springer Lecture Notes in
Artificial Intelligence, Vol. 2741, pp.~458--472, 2003.

\newpage

\section{\sc Refereed Workshop and Conference Publications Contd.}

M. Govindaraju, A. Slomenski, V. Choppella, R. Bramley and
  D. Gannon.  {\bf Requirements for and Evaluation of RMI
  Protocols for Scientific Computing}. In {\em {Proc. of the
  IEEE/ACM conference on SuperComputing (SC 2000), Nov
  2000}}.

B. Bose. M. Esen Tuna, and V. Choppella.  {\bf Tutorial on
Digital Design Derivation with DRS}.  In {\em {Proc. 1st
International Conf. on Formal Methods in Computer Aided
Design, (FMCAD '96), Palo Alto, CA, USA, Nov 1996}},
Springer Lecture Notes in Computer Science, Vol~1166, 1996.

P. Bradford, V. Choppella, and G. J. E. Rawlins.  %
%\url{http://dx.doi.org/10.1007/3-540-59175-3_85}
{\bf Lower
  Bounds on the Matrix Chain Order problem: Extended
  Abstract}.  In {\em {Proc. 2nd Latin American Symposium on
    Theoretical Informatics, (LATIN'95), Valparaiso, Apr
    1995}}.  Springer Verlag Lecture Notes in Computer
Science Vol.~911, 1995.

\section{\sc Refereed\\ Journal\\ Publications}

S.~Krishnan, S.~Krishnamoorthy, G.~Baumgartner, C-C.~Lam,
J.~Ramanujam, P.~Sadayappan and V.~Choppella.  {\bf
  Efficient Synthesis of Out-of-core Algorithms Using a
  Nonlinear Optimization Solver (Revised and Extended
  Version).}  {\em {Journal of Parallel and Distributed
    Computing}} Vol. 66. pp.~659-673, May~2006.  {\bf
  Invited submission}.

Alexander A. Auer, Gerald Baumgartner, David E. Bernholdt,
Alina Bibireata, Venkatesh Choppella, Daniel Cociorva,
Xiaoyang Gao, Robert Harrison, Sriram Krishnamoorthy,
Sandhya Krishnan, Chi-Chung Lam, Qingda Lu, Marcel Nooijen,
Russell Pitzer, J. Ramanujam, P. Sadayappan and Alexander
Sibiryakov.  {\bf Automatic code generation for many-body
electronic structure methods: the tensor contraction
engine}.  {\em Molecular Physics.} Vol.~104,~No.~2,
pp.~211-228, January 2006.

V. Choppella and C.T. Haynes.  {\bf Source-tracking
Unification (Revised and Extended Version)}.  {\em
{Information and Computation}} Vol.~201 Issue~2,
pp.~121-159, Sep~2005.  {\bf Invited submission}.

G. Baumgartner, A. Auer, D. Bernholdt, A. Bibireata,
V. Choppella, D. Cociorva, X. Gao, R. Harrison, S. Hirata,
S. Krishnamoorthy, S. Krishnan, C. Lam, M. Noojien,
R. Pitzer, J. Ramanujam, P. Sadayappan, A. Sibiryakov.  {\bf
Synthesis of High Performance Parallel Programs for a Class
of ab initio Quantum Chemistry Models}.  {\em {Proceedings
of the IEEE: Special Issue on Domain-Specific Program
Generation and Optimization}}, Vol.~93, No.~2, pp.~276--292,
February 2005.  {\bf Invited submission}.

K.~Rath, V.~Choppella and S.~D.~Johnson.  {\bf Decomposition
of Sequential Behavior using Interface Specification and
Complementation}.  In {\em {VLSI Design, Special Issue on
Decomposition}}, Vol. 3, Nos.~3-4, pp.~347--358, 1995.

% \section{\sc Journal and Conference Submissions}

% Philip Bradford and Venkatesh Choppella.  Fast Semi-Dyck
% Constrained Shortest Paths.  Submitted for review. 

\vspace{2em}

%% \section{\sc Papers in preparation}
%% % J. B. White, V. Choppella, D. E. Bernholdt.  Monadic synthesis
%% % of the NAS Multi-grid Benchmark.

%% Venkatesh Choppella.  {\bf Variable-free canonical forms for
%% Tensor Expressions}.

%% Venkatesh Choppella and Guillaume Marceau.  {\bf Graph Embeddings
%% for diagnosing Hindley-Milner type reconstruction}.

\newpage

\section{\sc Papers under review}

Venkatesh Choppella and T B Dinesh.  {\bf FOSS, Web 2.0 and
  Mashups as a Natural Learning Management Infrastructure}.
Tutorial proposal submitted to the 2nd IEEE Conference on
Technology for Education, Mumbai, Jul 2010.

Thulasi Ram Naidu P., Manisha Verma, Venkatesh Choppella and
Gangadhar Chalapaka.  {\bf Synthesizing Learning
  Environments}.  Submitted to the 2nd IEEE Conference on
Technology for Education, Mumbai, Jul 2010.

Venkatesh Choppella {\bf A case for Subversion in Academia}.
Submitted to the 2nd IEEE Conference on Technology for
Education, Mumbai, Jul 2010.

\vspace{2em}

\section{\sc Books in preparation}

An Introduction to the Principles of Programming.  With
T~B~Dinesh.

\vspace{2em}

\section{\sc Technical Reports}

V. Choppella, A. Sengupta, E. L. Robertson, S. D. Johnson.
Constructing and Validating Entity-Relationship Data Models
in the PVS Specification Language: A case study using a
text-book example.  Indiana University Computer Science
Technical Report TR632.  April 2006.

V. Choppella.  {A Compositionality Principle for Syntactic
Unification.}  July 2004. {\em Unpublished manuscript}.  

Venkatesh Choppella. Unification Source-tracking with
Application to Diagnosis of Type Inference.
(PhD. dissertation) {\em {Indiana University Computer
Science Tech. Report. \#566, Aug 2002}}.

A. Banerji, C. Bartolino, D. Beringer, V. Choppella,
K. Govindarajan, A. Karp, H. Kuno, M. Lemon, G. Pogossiants,
S. Sharma, S. Williams.  Web Services Conversation Language
(WSCL) 1.0 Hewlett-Packard Company, {\em {World Wide Web
Consortium Note, Mar 2002}}. \url{http://www.w3.org/TR/wscl10}

B. Bose, M. Esen Tuna, V. Choppella.  Derivational Reasoning
System: A Digital Design Derivation System for Hardware
Synthesis.  {\em {Contract NAS1-20414 National Aeronautics and
 Space Administration (NASA) SBIR Phase II Final
Report, Mar 1997}}.

V. Choppella and C. T. Haynes.  Diagnosis of Ill-Typed Programs,
{\em {Indiana University Tech. Report. \#426, Dec 1994}}.

Venkatesh Choppella.  Implementation of ML using the SECD
machine.  M.Tech thesis IIT Madras. 1987. 

\newpage

\section{\sc Thesis Supervision}

{\em Automatic generation and deployment of Network
  Configuration scripts}.
Gangadhar~Chalapaka. Post-Graduate Diploma in Information
Technology (PGDIT), IIITM-K 2009 (Expected).

{\em Rebuilding the Institute Network}.  V.~Asha~ Rose,
Girish~N~Gopal, Mithu~Mary~Kuruvilla.  MSIT, IIITM-K 2008.

{\em Building Instructional Technologies and Content for the
  Course Principles of Programming Course}.  Girish~N~Gopal,
Mithu~Mary~Kuruvilla.  MSIT, IIITM-K 2008. 

{\em Automatic Generation of Formal Specification of
  Entity-Relationship Diagrams}.  Alice~Joseph.  M.Tech
Vellore Institute of Technology 2008.  External Supervisor.

{\em Modeling Point Mutations in E-Coli Gene and their
  effect on fitness over successive generations}.
Nithya~Sam and Vimi~Soman.  Masters in Information
Technology (MSIT), IIITM-K 2007.  

{\em IT support for Palliative Care services with an
  e-learning platform and an electronic health record.}
Cibi Chacko, K.~Rejoy Bhaskar, V.~R.~Lekshmi and I.~Subha.
MSIT, IIITM-K 2007.

{\em Detecting system-breakins by comparing correlated
  frequency matrices}.  Anju~Pratap.  M.Tech. Computer
Science, Alagappa University 2007.  External Supervisor.

{\em Police Portal for Community Interaction: General
  Category Manipulation and Alert System}.  Jeena Premkumar.
Post Graduate Diploma in Information Technology (PGDIT),
IIITM-K 2005.

{\em Formal Specification of Police Portal's Complaint
  Module using Z and OCL}.  Sangram~Jena and Manish~Garg.
PGDIT, IIITM-K 2005. 

{\emph{Web Services for Agricultural Marketing System}}.
K.~M.~Manu~Prathab and P.~Roopiga.  MSc Computer Science,
Kerala University 2004.

{\em Implementation of Efficient Algorithms for Unification
  Debugging}.  M.~T.~Chitra and V.~G.~Suman.  MSc. Computer
Science, Kerala University 2004.

\vspace{2em}

\section{\sc Patents}

Cristina Lopes, Gregor Kiczales, John Lamping, Erik Hilsdale,
Venkatesh Choppella, and Taher Haveliwala.
\href{http://www.patentstorm.us/patents/6473895.html}
{Aspect-Oriented System Monitoring and Tracing}.  {\em {U.S.
    Patent No. 09/357,508.}} Filed 1999. Awarded April 2002.

% \newpage
\section{\sc Awards}

\href{http://www.manthanaward.com/winner2005.asp}{All India
Manthan Awards} Second Prize in the E-Governance category
for coordinating the Trivandrum City Police Portal for
Community Interaction \url{www.tvmcitypolice.org}, New
Delhi, India,~2005.

\section{\sc Awards Contd.}

Best Paper Award. International Parallel and Distributed
Processing Symposium (IPDPS), Albuquerque, New Mexico,
USA,~2004.

% \newpage

Best Paper Award  (Systems). Internationl Conference on High
Performance Computing (HiPC), Hyderabad, India,~2003.

DuPont Fellowship, Computer Science Dept., Indiana
University,~1988.

Merit Certificate for performance in the Joint Entrance
Examination, IIT Kanpur,~1981.

%\newpage

\section{\sc Grants}

European Commission.  Erasmus Mundus External Cooperation
Window. European Research and Educational Collaboration with
Asia Project for Academic Mobility 2008-2009.
\url{http://www.mrtc.mdh.se/eureca/}.  Institute
Coordinator.  10,000 Euro.

Govt. of Kerala, Dept. of Information Technology.  Centre
for Computational Biology.  January 2009.  Rs. 30 Lakhs.
Co-investigator.

Govt. of Kerala, Dept. of Information Technology.  Centre
for Computational Chemistry.  January 2009.  Rs. 25 Lakhs.
Co-investigator.

Govt. of Kerala, Dept. of Information Technology.
Innovation Centre for Open Standards in Software Engineering
Education.  January 2009.  Rs. 40 Lakhs.  Co-investigator.

IIITM-K internal grant.  Principles of Programming.
2008-2009.  Principal Investigator.  Rs. 500,000 (pending).

Ministry of Information Technology, Government of India.
Information Security Education and Awareness (ISEA)
2006-2011.  Principal Investigator at Participating
Institution IIITM-K.  Rs. 300,000 per annum. 

Government of Kerala.  Police Portal for Community
Interaction 2004-2005.  Rs. 2,900,000.  Co-investigator.


\section{\sc Professional Service}

Programme committee member, India Software Engineering
Conference (ISEC) February, 2011, Thiruvananthapuram, India.

Programme committee member, International Conference on
Distributed Computing and Internet Technologies (ICDCIT)
February, 2010, Bhubaneswar, India.

Programme committee member and reviewer, IEEE International
Conference on Software Engineering Education and Training
(CSEET) Feb 17-19, 2009, Hyderabad, India.

% Heap Reference Analysis by Amay Karkare

External reviewer for PhD Thesis, Computer Science, Indian
Institute of Technology, Bombay, Jan 2009.

Convener, Institute Information Technology and Services
Committee, IIITM-K.  Mar 2008 - Jan 2009.

\section{\sc Professional Service contd.}

Member, committee appointed by Kerala State IT Mission,
Govt.~of Kerala, to implement Public Key Infrastructure in
state government offices, 2008.


Reviewer, Journal of Parallel and Distributed Computing.
Elsevier. Aug 2008.

Reviewer, International Journal of Formal Computing.
Springer. Aug 2008.

Organizer, Free Map Workshop, IIITM-K, Feb 2008. 

Organizer, One day workshop on Pantoto: Building Information
Management Systems for Small and Medium Enterprises. 
IIITM-K, Feb 2008.

Programme and Organizing Committee member, IEEE workshop on
Connecting Computer Science to Domains, IIITM-K.  Dec~2007.

Convener, Institute Academic Affairs Committee, IIITM-K.
Aug 2006 - July 2007.

Moderator, Panel on Computer Science Teaching, National
workshop on Technology Enhanced Learning, Trivandrum,
Kerala, India.  Jan 5th-6th, 2007.

Panelist, Scilab in Science and Engineering Education.
Indo-French Workshop on Scilab, IIT Bombay.  Mar~8th,~2007.

Organizer, IEEE/CSI Workshop on Community Wireless
Networking, Trivandrum, Kerala, India, Dec 1st-2nd, 2006.

Programme Committee member, International Conference on
Advanced Computing and Communications (ADCOMM~05),
Coimbatore, India, Dec 14-17, 2005.

Programme Committee member, Free Software, Free Society: Three
nation conference on Free, Libre and Open Source Software,
Trivandrum India, May 2005.

Board Member, SPACE (Society for Promotion of Alternative
Computing and Employment), NGO for promoting Free and Open
Source Software in Kerala. Since 2004.

Anonymous referee for The Fifth International Conference on
Parallel and Distributed Computing, Applications and
Technologies (PDCAT~04), 2004.  

Acknowledged by the authors of the following books for
proof reading, comments  and technical assistance:\\
\begin{list2}
 \item G. Springer and D. P. Friedman.  {Scheme and the Art of
 Programming}.  {\em {MIT Press,~1989}}.
%%  \vspace{0.5em}
 \item D.P. Friedman, M. Wand and C.T. Haynes.  Essentials of
 Programming Languages, 1st Edition  {\em {MIT Press,~1991}}.
%%  \vspace{0.5em}
 \item Raymond Smullyan. G\"{o}del's Incompleteness Theorems.
 {\em {Oxford University Press,~1992}}.
%%  \vspace{0.5em}
 \item Jon Barwise and Lawrence S. Moss. Vicious Circles
 {\em {CSLI Stanford,~1997}}.
\end{list2}

% \section{\sc Programming Experience} 
% \begin{list2}

% \item Languages: Fortran, Lisp, C, Scheme, ML, Haskell,
%   Prolog, Java, Python, Javascript

% \item Internet Technologies:  J2EE, Spring, Ruby on Rails, Web 2.0

% \item Theorem Provers:  PVS

% \item Operating Systems:  Unix/Linux, Windows
% \end{list2}

\newpage

\section{\sc Professional Membership}

Computer Society of India

Indian Association for Research in Computer Science

\section{\sc Citizenship}
Citizen of India

\section{\sc Date of Birth}
Available upon request.

\section{\sc Languages}
English, Hindi, Telugu

\section{\sc References}
Available upon request.



\end{resume}
\end{document}




