\documentclass[margin,line]{res}
\usepackage[pdftex]{graphicx}
\usepackage[usenames,dvipsnames]{color}
%% \input{colordefs}
\usepackage[pdftitle={Dr. Shailaja Tetali's CV},%
colorlinks=true,% true
citecolor=black,%blue,%
urlcolor=navy%
]{hyperref}


%% \pagecolor{lightgoldenrodyellow}
%% \pagecolor{snow}

% see http://www.sci.usq.edu.au/staff/robertsa/LaTeX/usecolour.html
% on how to use predefined colors

% \color{Brown}


\oddsidemargin -.5in
\evensidemargin -.5in
\textwidth=6.0in
\itemsep=0in
\parsep=0in

\newenvironment{list1}{
  \begin{list}{\ding{113}}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.17in}}}{\end{list}}
\newenvironment{list2}{
  \begin{list}{$\bullet$}{%
      \setlength{\itemsep}{0in}
      \setlength{\parsep}{0in} \setlength{\parskip}{0in}
      \setlength{\topsep}{0in} \setlength{\partopsep}{0in} 
      \setlength{\leftmargin}{0.2in}}}{\end{list}}


\begin{document}

\name{Dr. Shailaja Tetali \vspace*{.1in}}

\begin{resume}
\section{\sc Contact Information}
\vspace{.05in}
\begin{tabular}{@{}p{2.5in}p{0.9in}l}
MLR-32, Mangalam Lane   & {\it Home Phone:}  & +91-471-272-6573 \\
Sasthamangalam         & {\it Mobile:}      & +91-934-931-2356 \\
Trivandrum             & {\it E-mail:}      & shailaja\_c@yahoo.com\\ 
Kerala 695 010, INDIA  & \\
%% {\it URL:}
%% \href{http://www.iiitmk.ac.in/~choppell/shailaja}{http://www.iiitmk.ac.in/{\textasciitilde}choppell/shailaja}\\     
\end{tabular}
% {www.iiitmk.ac.in/\verb+~+choppell}

\section{\sc Interests}
HIV/AIDS, Health education, Immunisation, Maternal and Child
Health, Adolescent health issues, Public health research and
health policy, Information Technologies and public health.

\section{\sc Recent and Current work}
%% \begin{list1}

A study on the effectiveness of the School AIDS
Education programme in Trivandrum Education District
(Jun-Oct '05, MPH dissertation).

Proposal to develop and commission a community portal
      for HIV related education, awareness monitoring and
      control programs: submitted to the Department of
      health, Government of Kerala in February 2006.

Proposal for a National workshop on Health
      informatics and medical education grid services over
      ISRO telemedicine network, to be jointly organized by
      IIITM-K and the Indian Space Research Organization in
      the second quarter of 2006.

Research study on doctors' perceptions regarding the
      social acceptance of male circumcision in Kerala,
      India (joint work with Harvard School of Public Health).
%% \end{list1}
%% \vspace{0.3in}

\section{\sc Education}

{\bf Sree Chitra Tirunal Institute for Medical Sciences and
Technology\/} (SCTIMST) Trivandrum, India\\

\vspace*{-.1in}
\begin{list1}
\item[] Masters in Public Health, December  2005.  
\begin{list2}
\vspace*{.05in}
\item Thesis:  \emph{A study on the effectiveness of the School AIDS
Education programme in Trivandrum Education District\/}
\item Supervisor:  Prof. T. K. Sundari Ravindran
\end{list2}
\end{list1}

{\bf Sri Ramachandra Medical College and Research Institute}, Chennai, India\\
%{\em Department of Computer Science and Engineering} 
\vspace*{-.1in}
\begin{list1}
\item[] Bachelor of Medicine and Bachelor of Surgery (MBBS),  March~1994
\end{list1}

\section{\sc Areas of\\ Training}
Epidemiology, Biostatistics, Quantitative and Qualitative
Research Methodology, Health System Management, Health
economics, Health policy, Health and the environment,
Health and development, Making pregnancy safer, Ethics in
health research, Gender issues in health research.

\section{\sc Areas of Experience}

Clinical treatment of patients

\vspace{-0.8em}

Health related program planning, management and monitoring.

\vspace{-0.8em}

Health education to couples regarding reproductive health
and to teens regarding adolescent health issues

\vspace{-0.8em}

Working in programme and related aspects with health care
providers, community members, field staff, and partner NGO's

\vspace{-0.8em}

Project related documentation

\vspace{-0.8em}

Technical support for building the
effective HIV / AIDS control among high-risk target
population

\vspace{-0.8em}

Developing concept notes, technical strategies, documentation and analysis

\vspace{-0.8em}

Research in Public health


%% \section{\sc Research Experience}


%% Sree Chitra Tirunal Institute of Medical Sciences and Technology,Trivandrum Jan 04 - 31 Dec 05
%% \begin{list1}
%%  \item[] Masters in Public Health dissertation work:
%%  Research on The effectiveness of the School AIDS Education
%%  Program in Trivandrum Education District June-Oct '05

%%  \item[] Research on Ethical dilemma of blood donation
%%  presented in the National Bioethics conference, Mumbai,
%%  November 25-27, 2005.

%%  \item[] Research on immunisation programs presented a paper
%%  on Falling immunisation rates in the Indian sub-continent-
%%  Possible effect of Pulse Polio and other causes in the 32nd
%%  National conference of PSM, held at Loni, Maharastra, from
%%  17th to 19th February 2005.

%%  \item[] Research on Occupational Exposure to Sharps-
%%  involved in project conceptualisation, design, data
%%  collection, analysis and report preparation.
%% \end{list1}

\section{\sc Work\\ Experience}
{\bf Indian Inst.\ of Info.\ Tech.\ \& Mgmt.\ -- Kerala} 
\vspace{-0.4cm}

{\em Senior Project Officer} \hfill {\bf Jan 2006 - }

\vspace{-0.2cm}

The work involves the incorporation of Information and
Communication Technologies (ICT) in the management of public
health programs.  Specifically, developing project
proposals, convening workshops, networking with governmental
and non-governmental organizations, providing technical
expertise while implementing projects on tele-health, HIV
portal for community interaction, and health informatics.

\section{\sc Voluntary Work}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf Hoosier Courts Pre-school} Indiana University, Bloomington,
Indiana, USA
\vspace{-0.4cm}

{\em Parent Teacher Volunteer} \hfill {\bf Mar 2001 - Aug
2002}

\vspace{-0.2cm}

%% Worked closely with children aged 3 to 5 and developed
%% their inter-personal skills.  Learnt about various aspects of
%% child psychology.

%\vspace{-.1cm}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf University Health Services} Indiana University,
Bloomington, Indiana, USA

\vspace{-0.4cm}

\emph{Health Education Volunteer}\hfill {\bf Aug 2000 - Dec 2000}

\vspace{-0.2cm}

Coordinated interactive health education programs for Indiana
University women.  Lectured on nutrition during pregnancy,
contraception services, and children's health including first
aid.

\section{\sc Clinical\\ Practice}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
{\bf Sooriya Hospital, Vadapalani, Chennai, India}

\vspace{-0.4cm}

\emph{Duty Medical Officer, Emergency Medicine}\hfill {\bf
  Jan~1994 - Dec~1994}

\vspace{-0.2cm}

%% Attended to emergency cases and assisted in the conducting of
%% emergency surgeries.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf Adipathi Nursing Home, Velachery, Chennai, India}

\vspace{-0.4cm}

\emph{Duty Medical Officer}\hfill {\bf  Jan~1995 - Jun~1995}

\vspace{-0.2cm}

%% Attended to and assisted in the treatment of patients.  

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

{\bf Chennai, India}

\vspace{-0.4cm}

\emph{Private Practioner}\hfill {\bf Jan~1993 - Jan~1995}\\

\vspace{-0.2cm}

%% Provided ante-natal care, immunizations and routine health care
%% people in the local community.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


%\vspace{-.1cm}


\section{\sc Conference Participation}

National Student and Youth Parliament, Special session on HIV/
AIDS, New Delhi, November 2nd to 6th 2004.  Resource person
representing the state of Andhra Pradesh.  Moderated discussions
on HIV and AIDS among adolescents.

\section{\sc Journal Articles}

\emph{Occupational exposure to sharps and splash: Risk among
  health care providers in three tertiary care hospitals in
  South India}.  Shailaja Tetali and Lincoln Choudhury.
Accepted for publication in The Indian Journal of
Occupational and Environmental Medicine, February~2006.

\emph{Ethical challenges in voluntary blood donation in
Kerala, India}.  Submitted to the British Journal of Medical
Ethics, January~2006.

\section{\sc Workshop and Conference Presentations }

% \emph{Road Safety Is No Accident}. World Health Day 2004,
% Apr~6~2004, SCTIMST, Trivandrum, India.


\emph{Hospital injuries: Risk among health care providers in
South India}.  Shailaja Tetali, Lincoln Choudhury.  Accepted
at the 8th World Conference on Injury Prevention and Safety
Promotion 2006, ICC Durban, South Africa, April~2-5,~2006.

\emph{Knowledge empowered communities and their role in the
control of HIV}.  Lincoln Choudhury, Shailaja Tetali, KR
Srivathsan. International conference on urban health
initiatives, Surat, India, February 9-11,~2006.

\emph{The burden of road traffic accidents on Kerala's
health system}.  Shailaja Tetali. International conference
on urban health initiatives, Surat, India, February 9-11,~2006.

\emph{Urban health systems: challenges and solutions.}
Lincoln Choudhury, Shailaja Tetali. International conference
on urban health initiatives, Surat, India, February
9-11,~2006.

\emph{The cost of compromising safe injection practices is
high, but avoidable.}  Shailaja Tetali, Lincoln
Choudhury. Joint National conference of IAPSM and IAPH,
Tirupati, January~21-25,~2006.
\newpage
\section{\sc Workshop and Conference Presentations (contd.)}

\emph{Falling Immunization Rates In The Indian Subcontinent: The
  Possible Effect Of Pulse Polio Campaigns And Other Reasons}.
Shailaja Tetali and Lincoln~Choudhury.  32nd Annual National
Conference of Indian Association of Preventive and Social
Medicine, Loni, Maharashtra, India,  February~17-19,~2005.

\emph{Ethical Challenges In Voluntary Blood Donations}.  Lincoln
Choudhury and Shailaja Tetali.  National Bioethics Conference,
Mumbai, India, November~25-27,~2005.

\emph{Risk of Occupational Exposure to Sharps among Female
  Health Care Providers}.  Shailaja Tetali and Lincoln
Choudhury.  The Fourth International Congress on Work, Women and
Health, New Delhi, India,  November~27-30,~2005.


\section{\sc Technical Reports}

\emph{Action Plan For Tsunami Preparedness}. Submitted to the
Government of Kerala in January 2005 after surveying Tsunami
affected areas of Kerala and Tamil Nadu, India.  Co-author.

\emph{Falling Immunization Rates in the Indian Subcontinent: the
  Possible Effect of Pulse Polio Campaigns and Other Reasons}.
With Dr. Lincoln Choudhury.  


\section{\sc Distinctions}
College 1st in Forensic Medicine.

\section{\sc Computer Skills} 
\begin{list2}
\item MS Word, Excel and Power Point.
\item Data entry and statistical analysis using EPI Info and SPSS
\end{list2}

\section{\sc Languages}

English, Hindi, Telugu, Tamil and spoken Malayalam. 

\section{\sc Citizenship}

Citizen of India

\section{\sc References}
Dr.~Richard~A.~Cash, Senior lecturer Harvard School Of
Public Health, Boston, Massachusetts, USA. E-mail:~{\tt
racash@hsph.Harvard.edu}

\vspace{-0.5em}

Prof.~T.K.~Sundari~Ravindran, Consultant, WHO and Honorary
Professor, Achuta Menon Center for Health Science Studies,
Sree Chitra Tirunal Institute for Medical Sciences and
Technology, Trivandrum, Kerala 695~011, India.
E-mail:~{\tt ravindrans@usa.net}

\vspace{-0.5em}

Dr.~K.R.~Thankappan, Head of the department, Achuta Menon
Center for Health Science Studies, Sree Chitra Tirunal
Institute for Medical Sciences and Technology, Trivandru,
Kerala 695~011, India.  E-mail:~{\tt thank@sctimst.ac.in}
\end{resume}
\end{document}




